Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
Add mention about degenerated tags in NER metric

\begin{table}
\small
\begin{tabular}{llp{8cm}}
Entity & Count & Description\\    
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: "Alibert (Prosper)", "Allamand frères et Hersent", "Heurtemotte (Vve)", etc. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: "O. \scalerel*{\includegraphics{./images/LH.png}} {H}" for "Officier de la Légion d'Honneur" or "\scalerel*{\includegraphics{./images/GMLondon.png}}{H}" to represent the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarized in the single concept of activity. E.g.: "horlogerie", "export en tous genres", "Conseiller d'Etat", "propriétaire".\\
LOC & 9709 & mostly street names ("r. de la Jussienne"), but may also be neighborhoods ("Marais du Temple") or any indirect spatial references ("au Palais Royal").\\
CARDINAL & 8747 & a street number, as part of an address ("16", "5 bis"), or a range of numbers (e.g. "23-25" or "5 à 9").\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. "boutique", "atelier", "fab." or "dépôt". \\
\end{tabular}
\caption{Entities to recognize in the dataset.}
\label{tab.entities}
\end{table}

@@

The evaluation process illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.

\joseph{FIXME say we need to discard some entries}

>>>>

\begin{table}
\caption{Entities to recognize in the dataset.}
\label{tab.entities}
\small
\begin{tabular}{llp{8cm}}
Entity & Count & Description\\    
PER & 8788 & a person name or a business name, usually referred to as several person names. First names, initials, or civility mentions are included. E.g.: "Alibert (Prosper)", "Allamand frères et Hersent", "Heurtemotte (Vve)", etc. \\
TITLE & 483 & an honorary title, either text, glyphs or a combination of the two. E.g: "O. \scalerel*{\includegraphics{./images/LH.png}} {H}" for "Officier de la Légion d'Honneur" or "\scalerel*{\includegraphics{./images/GMLondon.png}}{H}" to represent the Great Medal at the London exhibition.\\
ACT & 6472 & the profession or social status of a person summarized in the single concept of activity. E.g.: "horlogerie", "export en tous genres", "Conseiller d'Etat", "propriétaire".\\
LOC & 9709 & mostly street names ("r. de la Jussienne"), but may also be neighborhoods ("Marais du Temple") or any indirect spatial references ("au Palais Royal").\\
CARDINAL & 8747 & a street number, as part of an address ("16", "5 bis"), or a range of numbers (e.g. "23-25" or "5 à 9").\\
FT & 43 & a geographic entity type, used to give more details on a location, e.g. "boutique", "atelier", "fab." or "dépôt". \\
\end{tabular}
\end{table}

@@

The evaluation process illustrated on~\cref{fig.eval-ocr-ner}. The OCR text and the groundtruth are first aligned to
evaluate the OCR accuracy. As there are 11 mismatches over 56 aligned characters, the CER is thus 24\%. This alignment
is then used to back-project the groundtruth tags to build the tagged NER-\emph{target}. Finally, the NER system runs on the
OCR text; its output is compared to the NER groundtruth. There is only 2 over 3 tags matching in the prediction (precision),
while only 2 over 4 entities are matched in the reference (recall). It follows an overall f-score of 0.4.
%
A side-effect of tag projections is that is can produce degenerated tags, i.e. empty or containing only spaces.
In such cases, the corresponding entries must be removed from the dataset for NER evaluation,
and only the intersection of the sets of valid entries must be used to compare NER systems on multiple OCR predictions or references.
